---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation
options(scipen = 999) 

```

# Dependencies

```{r}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)

```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("Whole sample" = 1)) |> # note that you can add header rows to tables like this. The "1" indicates the number of columns the header should span. The sum of these numbers must equal the number of columns or you'll get an error.
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Age

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)

```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations

### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}


```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))

```

# Analyses & hypothesis tests

## Cronbach's Alpha AMP

```{r}

library(psych)

alpha(subset(data_processed_after_exclusions, select = c(like, positive, prefer)), check.keys = TRUE)


```

## Interpretation

raw alpha is .88, which is considered high and therefore good reliability.

## Hypothesis 1: Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}
# self-reported evaluation as dependent variable
ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

# amp score as dependent variable
ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: <https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html>

\TODO add axial histograms to a scatter plot. Split both the scatter plot and the histograms by gender.

```{r}
library(ggExtra)
library(scales) #for viridis 
# histogram by gender
histogram <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation, colour = gender)) +
  geom_point() +
  geom_smooth(aes(color = gender), method = "lm", se = FALSE) +  # Regression line by gender 
  scale_colour_manual(name = "gender",
                         values = c("female" = "#73D055FF", "male" = "#404788FF", "nonbinary" = "#FDE725FF")) +
  theme(legend.position = c(.15, .7), legend.background = element_rect(color = "black",
                                                                       size = 0.5)) +
  labs(x = "Self-report Evaluations", y = "AMP Score",
title ="Relationship")

ggMarginal(histogram, type = "histogram", groupColour = TRUE, groupFill = TRUE)

# density plot by gender
density <- ggplot(data_processed_after_exclusions, 
       aes(x = mean_evaluation ,
           y = AMP_score, colour = gender)) +
  geom_point() +
  geom_smooth(aes(color = gender), method = "lm", se = FALSE) +  # Regression line by gender 
  scale_colour_manual(name = "gender", labels = c("Female", "Male", "Non-binary"),
                         values = c("female" = "#73D055FF", "male" = "#404788FF", "nonbinary" = "#FDE725FF")) +
  theme(legend.position = c(.2, .20), legend.background = element_rect(color = "black",
                                                                       size = 0.5))

ggMarginal(density, type = "density", groupColour = TRUE, groupFill = TRUE)

```

#### Labelled points

Label points using ggrepel: <https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html>

\TODO Label the points in a scatter plot using their participant codes.

```{r}

#label all points

library(ggrepel)

p <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation, label = subject)) +
  geom_jitter(color = "red") 
  
p1 <- p + geom_text() + labs(title = "geom_text()")
p2 <- p + geom_text_repel() + labs(title = "geom_text_repel()")

gridExtra::grid.arrange(p1, p2, ncol = 2)


#only labeling outliers





```

#### Magnify areas

Magnify areas of your plot with ggmagnify: <https://hughjonesd.github.io/ggmagnify/>

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}

#install.packages("remotes")
#remotes::install_github("hughjonesd/ggmagnify")

library(ggplot2)
library(ggmagnify)


from <- c(xmin = 0.45, xmax = 0.68, ymin = 0.85, ymax = 1.3)
# Names xmin, xmax, ymin, ymax are optional:
to <- c(xmin= 0.00, xmax = 0.25, ymin = 2, ymax= 3.3)


ggpi <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation, label = subject)) +
              geom_jitter()

ggpi + geom_magnify(from = from, to = to, colour = "black", linewidth = 0.7, proj.linetype = 3)




```

### Test

\TODO

```{r}

correlation_H1 <- cor.test(data_processed_after_exclusions$mean_evaluation,
                      data_processed_after_exclusions$AMP_score,
                      method = "pearson")
correlation_H1

```

### Interpretation

The pearson correlation yields a value of -0.124

## Self-reported evalautions differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}

#split histogramm
ggplot(data_processed_after_exclusions, 
       aes(x = mean_evaluation,
            colour = gender)) +
  geom_histogram(binwidth = 1) +
  scale_colour_discrete(name = "gender",
                      labels = c("male", "female", "non-binary"))



#split violine
# how to install the introdataviz package to get split and half violin plots
#devtools::install_github("psyteachr/introdataviz")

ggplot(data_processed_after_exclusions, aes(x = gender, y= mean_evaluation)) +
  geom_violin() +
  geom_boxplot(width = .2, fatten = NULL) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1) +
  theme_minimal()


library(introdataviz)
ggplot(data_processed_after_exclusions, aes(x = "", y = mean_evaluation, fill = gender)) +
  introdataviz::geom_split_violin(alpha = .4, trim = FALSE) +
  geom_boxplot(width = .2, alpha = .6, fatten = NULL, show.legend = FALSE) +
  stat_summary(fun.data = "mean_se", geom = "pointrange", show.legend = F, 
               position = position_dodge(.175)) +
  scale_x_discrete(name = "gender", labels = c("male", "female", "non-binary")) +
  scale_y_continuous(name = "self-report") +
  theme_minimal()


#split raincloud plot
rain_height <- .1

library(ggplot2)
library(magrittr)
ggplot(data_processed_after_exclusions, aes(x = "", y = mean_evaluation, fill = gender)) +
  # clouds
  introdataviz::geom_flat_violin(trim=FALSE, alpha = 0.4,
    position = position_nudge(x = rain_height+.05)) +
  # rain
  geom_point(aes(colour = gender), size = 2, alpha = .5, show.legend = FALSE, 
              position = position_jitter(width = rain_height, height = 0)) +
  # boxplots
  geom_boxplot(width = rain_height, alpha = 0.4, show.legend = FALSE, 
               outlier.shape = NA,
               position = position_nudge(x = -rain_height*2)) +
  # mean and SE point in the cloud
  stat_summary(fun.data = mean_cl_normal, mapping = aes(color = gender), show.legend = FALSE,
               position = position_nudge(x = rain_height * 3)) +
  # adjust layout
  scale_x_discrete(name = "", expand = c(rain_height*3, 0, 0, 0.7)) +
  scale_y_continuous(name = "self-report") +
  coord_flip() +
  # custom colours and theme
  scale_fill_brewer(palette = "Dark2", name = "gender") +
  scale_colour_brewer(palette = "Dark2") +
  theme_minimal() +
  theme(panel.grid.major.y = element_blank(),
        legend.position = c(0.8, 0.8),
        legend.background = element_rect(fill = "white", color = "white"))



```

### Test

\TODO

```{r}

library(stats)
t.test(data_processed_after_exclusions$mean_evaluation ~ data_processed_after_exclusions$gender, var.equal= TRUE, alternative= "two.sided")#sig.: men and women differ significantly on the
#mean self-report evaluations 


```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}

#split histogramm
data_processed_after_exclusions <- data_processed_after_exclusions |> 
  dplyr::filter(gender == "male" | gender == "female") |> 
  mutate(gender = as.factor(gender)) |> 

p1 <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
            colour = gender)) +
  geom_histogram(binwidth = 0.1) +
  scale_colour_discrete(name = "gender",
                      labels = c("male", "female", "non-binary"))



#split violin

p2 <- ggplot(data_processed_after_exclusions, aes(x = "", y = AMP_score, fill = gender)) +
  introdataviz::geom_split_violin(alpha = .4, trim = FALSE) +
  geom_boxplot(width = .2, alpha = .6, fatten = NULL, show.legend = FALSE) +
  stat_summary(fun.data = "mean_se", geom = "pointrange", show.legend = F, 
               position = position_dodge(.175)) +
  scale_x_discrete(name = "gender", labels = c("male", "female", "non-binary")) +
  scale_y_continuous(name = "self-report") +
  theme_minimal()





```

### Test

\TODO

```{r}


data_processed_after_exclusions <- data_processed_after_exclusions |>
  mutate(gender = as.factor(gender)) |> 
  dplyr::filter(gender == "male" | gender == "female")

library(stats)
t.test(data_processed_after_exclusions$AMP_score ~ data_processed_after_exclusions$gender, var.equal= TRUE, alternative= "two.sided")


```

## Combining plots

Combine plots using patchwork: <https://patchwork.data-imaginist.com/>

\TODO Combine at least three of the above plots into one.

```{r}
#install.packages("devtools")
#devtools::install_github("thomasp85/patchwork")

library(devtools)
library(patchwork)


p1 + p2



```

## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

ggsave("combined_plot.pdf", plot = last_plot())

ggsave("combined_plot.png", plot = last_plot(),dpi = 300)

```

# Session info

```{r}

sessionInfo()

```
