---
title: "Plot assignment"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(naniar)

```

# Load Data

```{r}
dat_raw <- read_delim("data/data.csv", delim = ";", 
    escape_double = FALSE, trim_ws = TRUE) |> clean_names() |> 
  replace_with_na_all(condition = ~.x == 99)
View(dat_raw)

```

# Instructions

The goal of this exercise is to produce both good and bad examples of plots *and to be explicit about what makes them good or bad*.

The data can be real or fabricated. The plots can convey realistic or silly messages - but they must convey them clearly. You can get real data from many sources. A good one is the open science framekwork (osf.io). You can also simply make up data, either by hand or using simulation functions (e.g., `rnorm`) or the many simulation packages. If simulating data, ensure that you (a) use set.seed() to make it reproudbile, and (b) save a copy of the final data that you're using to disk and then reload it in the script so that the plot is reproducible.

The goal is neither to reproduce the types of plots that you most often see in journals (bar plots, etc.) nor to use a very fancy looking plot just for the sake of it - if it is very unlikely that you'd ever be able to use the plot to convey a research finding in an article, blog, poster, tweet, infographic or otherwise, it's probably not a good choice either.

# To do

-   The plots must be reproducible. Provide the data as well as the code to reporduce them.

-   The plots should also be saved as individual images (pdf or png).

-   Under each plot, here in the RMarkdown, briefly explain what types of analysis the plot is suitable for, what elements of the results the plot attempts to clearly convey.

-   For the bad plot, do the opposite: emphasise what features of the results the plot obscures or makes unclear. In doing so, communicate to me that you understand what makes a good plot to convey the results of quantiative analyses to viewers.

Consider making use of the many extensions to ggplot2, e.g.:

-   <https://r-graph-gallery.com>
-   <https://krzjoa.github.io/awesome-r-dataviz/#/>
-   ggdist <https://mjskay.github.io/ggdist/>
-   ggrepel
-   ggpubr
-   see
-   ggsignif
-   and others: <https://exts.ggplot2.tidyverse.org/gallery/>

# Good plot

```{r}

# Data transforming
dat <- dat_raw |> 
  mutate(dep = (dep1 + dep2 + dep3 + dep4)/4, 
         ig = (ig + igphotos1 + igphotos2)/3, 
         inter = (inter1 + inter2 + inter3 + inter4 + inter5)/5, 
         app = (app1 + app2 + app3 + app4 + app5 + app6 + app7 + app8 + app9 + app10)/10, 
         self = (self1 + self2 + self3 + self4 + self5)/5, 
         schem = (schem1 + schem2 + schem3 + schem4 + schem5 + schem6 + schem7 + schem8 +
                    schem9 + shcem10)/10, 
         height = (height/100),
         girl = as.character(girl), exp = as.factor(exp),
         bmi_new = round_half_up((weight/(height)^2), digits = 2)) |> 
  select(exp, girl, age, tiredness, sleep, dep, ig, inter, app, self, schem, bmi_new) |> 
  filter(bmi_new < 50, bmi_new > 10)
  
  
      
# correlation between depression and bmi
ggplot(dat, aes(x = dep, y = bmi_new, colour= girl)) + 
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_discrete(name = "Sex", labels = c("Boy", "Girl")) +
  theme_grey()



# correlation between depression and self-image
ggplot(dat, aes(x = self, y = dep, colour= girl)) + 
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_discrete(name = "Sex", labels = c("Boy", "Girl")) +
  theme_grey()





#raincloud plot
rain_height <- .1
library(introdataviz)
ggplot(dat, aes(x = "", y = dep, fill = girl)) +
# clouds
introdataviz::geom_flat_violin(trim = FALSE, alpha = 0.4, 
                                position = position_nudge(x = rain_height + .05)) +
  geom_point(aes(colour = girl),
             size = 2, alpha = .5, show.legend = FALSE, 
             position = position_jitter (width = rain_height, height = 0)) + # boxplots
  geom_boxplot(width = rain_height,
               alpha = 0.4, show.legend = FALSE, outlier.shape = NA, 
               position = position_nudge(x = -rain_height*2)) +
# mean and SE point in the cloud 
  stat_summary(fun.data = mean_cl_normal, mapping = aes(color = girl), show.legend = FALSE,
               position = position_nudge (x = rain_height *3)) +
#layout
  scale_x_discrete(name = "", expand = c(rain_height*4, 0, 0, 0.7)) + 
  scale_y_continuous(name = "Depression", breaks = seq(1, 5, 1), limits = c(1, 5)) +
  coord_flip() +
  facet_wrap(~ factor(exp, levels = c("0", "1"), 
                      labels = c("No Social Media", "Social Media Exposure")),
                            nrow = 2) +
  scale_fill_viridis_d(option = "H", name = "Gender", labels = c("Boys", "Girls"), begin = 0.2,
                       end = 0.8) +
  scale_colour_viridis_d(option = "H", begin = 0.2,
                       end = 0.8) +
  labs(title = "Depression Scores", subtitle = "split for gender and social media exposure" )+
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
                          legend.position = c(0.90, 0.96), 
                          legend.background = element_rect(fill = "white", color = "white"))


library(ggExtra)
library(scales) #for viridis 
# histogram by gender
ggplot(dat, aes(x = self, y = dep, colour = girl)) +
  geom_point() +
  geom_smooth(aes(color = girl), method = "lm", se = FALSE) + # Regression line by gender 
  scale_color_discrete(name = "Sex", labels = c("Boy", "Girl")) +
  theme(legend.position = c(.15, .7), 
        legend.background = element_rect(color = "black", fill = "white", size = 0.5)) +
  labs(x = "Self-image (likert-scale)", y = "Depression Score (likert-scale)",
title ="Relationship") +
  theme_minimal()

#Write to desk

ggsave("plot_good_AngelaOppenberg.pdf", plot = last_plot(), dpi = 300)


```

-   it contains information about the shape and variability of the distribution

-   x-axis is explicit

-   intuitive coloring

-   a titel

# Bad plot

```{r}

ggplot(dat, aes(x = exp, y = dep, fill = girl)) +
geom_bar(stat="identity", position= position_dodge())

#Write to desk
ggsave("plot_bad_AngelaOppenbergt.pdf", plot = last_plot(), dpi = 300)

```

This plot is bad because

-   it contains no information about the shape or variability of the distribution

-   x- and y-axis are not explicit

-   label girl not good and color misleading: blue for girl and pink for box

-   no titel

# Write to disk

Write to disk as a .pdf or .png.

Name them "plot_good\_[yourname]" and "plot_bad\_[yourname]".

```{r}




```

# Session info

```{r}

sessionInfo()

```
